COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd

    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

@@

@@

@@

>>>>

    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

@@

    # calculate the mean and sd of hit rate and false alarm rate per n-back level i

@@

      # z-transform each subject j's hit rate and false alarm rate within the level i

@@

```{r Hypothesis_1b, echo=FALSE, message=FALSE, warning=FALSE}

  # H1b: Performance measured by reaction time declines with increasing n-back level.

  rt <- data.frame(subject = character(), level = double(), meanrt = double())

  # calculate mean reaction time per participant per level

    meanrt <- mean(data_nback$rt[which(data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          meanrt = meanrt)
    rt <- rbind(rt, newdata)

  # ANOVA with three linear contrasts, contrasting the mean rt of two n-back levels (2,3,4) at a time

      h2a_data <- rt[rt$level != 1,]
      h2a_data$level <- as.factor(h2a_data$level)

      contrasts(h2a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))

      hypothesis2a_anova <- summary(aov(h2a_data$meanrt ~ h2a_data$level))
      hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$meanrt ~ h2a_data$level))
      remove(h2a_data)
